\chapter{Introduction}
The technological evolution of recent decades has profoundly transformed the business landscape, making IT solutions a crucial factor for the success of enterprises. In this context, Elmec Informatica S.p.A. stands out as a significant player in the Information Technology sector in Italy. Founded in 1971 and headquartered in Varese, Elmec combines extensive industry experience with a strong focus on innovation, offering services and solutions that cover a wide range of business needs, offering advanced IT solutions for medium and large enterprises. 

The company manages four datacenters (including one Tier IV certified), provides Hybrid IT services, digital workspace and Device-as-a-Service solutions, and is a key partner for cybersecurity and regulatory compliance. With over 450 certified technicians, Elmec integrates cloud technologies (in collaboration with AWS and GAIA-X), promotes environmental sustainability, and stands out for its innovation through its Technological Campus and ongoing investments in professional training.

The primary context of this internship revolves around the redesign and enhancement of the existing \textit{Service Request Portal (SRP)}, which is essential for managing client service requests efficiently.

A Service Requests is a formal request submitted by a customer to obtain specific services or actions within their IT infrastructure. These requests can encompass a wide range of activities, from creating new user accounts in the Active Directory system to managing user permissions, resetting passwords, and deploying software updates.

Various challenges have been identified within the current architecture, particularly concerning the dynamic forms used by customers for submitting the service requests, the management of customizable fields, and the integration with external data sources.

The main objectives of this internship are:
\begin{itemize}
    \item \textbf{Analysis of the Existing System}: Conduct a comprehensive analysis of the current state of the SRP system, identifying weaknesses and inefficiencies that hinder its performance and user experience;
    \item \textbf{Architectural redesign}: Propose and implement a complete architectural redesign of the system;
    \item \textbf{Modular and Scalable Solution}: Design a modular and scalable solution that can accomodate various client-specific configurations;
    \item \textbf{Migrations}: Plan and execute a full migration of databases and other company services/platforms that use SRP.
    \item \textbf{Fine-tuned LLMs integration}: Explore opportunities for integrating specifically fine-tuned LLM systems into the SR workflow.    
\end{itemize}